Pruning Subsequence Search with Attention-Based Embedding

### 2015-09-24 paper.tex
Add paragraph on ISMIR paper

>>>>

In \cite{raffel2015large}, a more general approximate method is proposed where a neural network model is used to map and downsample sequences of feature vectors to shorter sequences of bit vectors.
Computing the distance between bit vectors can be achieved by a single exclusive-or operation followed by a table lookup, so this approach vastly improves the efficiency of the local distance calculations involved in DTW.
Furthermore, downsampling the sequences gives quadratic speed gains.
In an experiment matching transcriptions of musical pieces to audio recordings in a large database, using this method allowed for 99\% of the entries in the database to be pruned with high confidence.
However, this approach still relies on DTW which is quadratic-time and therefore provides room for efficiency improvements.
